Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-04 ms.tex
Added Simulation section

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{yfonts}

@@

\subsubsection{Simulation}
We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters). yadda yadda yadda.

@@

In standard HOD models, there are two types of galaxies: centrals and satellites. The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy. So occupation statistics of central galaxies are specified by the first moment, which we model as

\begin{equation}
\label{eq:ncen}
\langle N_{\mathrm{cen}} \rangle(M) =
        \frac{1}{2}\left( 1 +
        \mathrm{erf}\left( \frac{\log_{10}M -
        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
\end{equation}
For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ a central galaxy is assigned to each halo whose random number is less than the corresponding value of $\langle N_{\mathrm{cen}} \rangle(M);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(M)$ are left devoid of centrals.

We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
\begin{equation}
\label{eq:nsat}
\langle N_{\rm sat}\rangle(M) = \left( \frac{M - M_0}{M_1} \right)^{\alpha}. 
\end{equation}

@@

We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
\begin{equation}
\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
\end{equation}
where $\tilde{r} = r/\rvir$ and $g(y) = \rm{ln}(1+y) - y / (1+y).$

@@

>>>>

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{yfonts}

@@

\subsubsection{Simulation}
All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ and with a box size of $250$ ${\rm Mpc}/h$ and a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.

We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}. In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.

@@

In standard HOD models, there are two types of galaxies: centrals and satellites. The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only either zero or one central galaxy. So occupation statistics of central galaxies are specified by the first moment of $P(\ncen|\mvir)$, which we model as

\begin{equation}
\label{eq:ncen}
\langle N_{\mathrm{cen}} \rangle(\mvir) =
        \frac{1}{2}\left( 1 +
        \mathrm{erf}\left( \frac{\log_{10}\mvir -
        \log_{10}M_{\rm min}}{\sigma_{\log_{10}M}} \right) \right)
\end{equation}
For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \rangle(\mvir);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(\mvir)$ are left devoid of centrals.

We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
\begin{equation}
\label{eq:nsat}
\langle N_{\rm sat}\rangle(\mvir) = \left( \frac{\mvir - M_0}{M_1} \right)^{\alpha}. 
\end{equation}

@@

We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
\begin{equation}
\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
\end{equation}
where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$

@@

%------------------------------------------------
\section{Acknowledgements}
\label{section:acknowledgements}
%------------------------------------------------

The authors gratefully acknowledge the Gauss Centre for Supercomputing e.V. (www.gauss-centre.eu) and the Partnership for Advanced Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the MultiDark simulation project by providing computing time on the GCS Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ, www.lrz.de). The Bolshoi simulations have been performed within the Bolshoi project of the University of California High-Performance AstroComputing Center (UC-HiPACC) and were run at the NASA Ames Research Center.
